Signed Peripherality Functions for Multivariate Statistical Inference

### 2018-03-23 MS-new/7_Appendix.tex
.

\begin{proof}[Proof of Proposition \ref{proposition:SignTest}]
Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $E (w(\bfZ) \bfS (\bfZ))$. For spherically symmetric $\bfZ$, $w(\bfZ)$ depends on $\bfZ$ only through its norm. Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $E (w(\bfZ) \bfS (\bfZ)) = E w(\bfZ). E \bfS (\bfZ)$. The same kind of decomposition holds for $Cov(w(\bfZ) \bfS(\bfZ))$.

We can now simplify the approximate local power $\beta_{n,w}$ of the level-$\alpha$ ($0 < \alpha < 1$) test based on $T_{n,w}$:
%
\begin{eqnarray*}
\beta_{n,w} &=& K_p \left( \chi^2_{p,\alpha} + n (E (w(\bfZ) \bfS (\bfZ))^T \right.\\
&& \left. [ E (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (E (w(\bfZ) \bfS (\bfZ)) \right)\\
&=& K_p \left( \chi^2_{p,\alpha} + \frac{E^2 w(\bfZ)}{Ew^2(\bfZ)}. E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) \right)
\end{eqnarray*}
%
where $K_p$ and $\chi^2_{p,\alpha}$ are distribution function and upper-$\alpha$ cutoff of a $\chi^2_p$ distribution, respectively. Since $E^2 w(\bfZ) \leq Ew(\bfZ)$, $\beta_{n,w}$ the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + E\bfS(\bfZ)^T [Cov(\bfS(\bfZ)]^{-1} E\bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic. Equality is of course achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
\end{proof}

@@

\begin{table}[b]
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
\label{table:FSEtable2}
\end{table}

\begin{table}[b]
\begin{footnotesize}
   \begin{tabular}{c|cc|ccc|ccc}
    \hline
    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
\label{table:FSEtable3}
\end{table}

>>>>

\begin{proof}[Proof of Proposition \ref{proposition:SignTest}]
Under contiguous alternatives $H_0: \bfmu = \bfmu_0$, the weighted sign test statistic $T_{n,w}$ has mean $\BE (w(\bfZ) \bfS (\bfZ))$. For spherically symmetric $\bfZ$, $w(\bfZ)$ depends on $\bfZ$ only through its norm. Since $\| \bfZ \|$ and $\bfS(\bfZ)$ are independent, we get $\BE (w(\bfZ) \bfS (\bfZ)) = \BE w(\bfZ). \BE \bfS (\bfZ)$. A similar decomposition holds for $\BV (w(\bfZ) \bfS(\bfZ))$.

We can now simplify the approximate local power $\beta_{n,w}$ of a level-$\alpha$, $0 < \alpha < 1$, test based on $T_{n,w}$:
%
\begin{align*}
\beta_{n,w} &= K_p \left( \chi^2_{p,\alpha} + n (\BE (w(\bfZ) \bfS (\bfZ))^T
[ \BE (w^2(\bfZ) \bfS (\bfZ) \bfS (\bfZ)^T) ]^{-1} (\BE (w(\bfZ) \bfS (\bfZ)) \right)\\
&= K_p \left( \chi^2_{p,\alpha} + \frac{\BE^2 w(\bfZ)}{\BE w^2(\bfZ)}. \BE\bfS(\bfZ)^T [\BV \bfS(\bfZ)]^{-1} \BE \bfS(\bfZ) \right),
\end{align*}
%
where $K_p$ and $\chi^2_{p,\alpha}$ are distribution function and upper-$\alpha$ cutoff of a $\chi^2_p$ distribution, respectively. Since $\BE^2 w(\bfZ) \leq \BE w(\bfZ)$, the largest possible value of $\beta_{n,w}$ is $K_p ( \chi^2_{p,\alpha} + \BE \bfS(\bfZ)^T [\BV \bfS(\bfZ)]^{-1} \BE \bfS(\bfZ) )$, the approximate power of the unweighted sign test statistic. Equality is achieved when $w(\bfZ)$ is a constant independent of $\bfZ$.
\end{proof}

@@

\begin{table}[t]
\begin{footnotesize}
    \begin{tabular}{c|cc|ccc|ccc}
    \hline
    $F$ = Bivariate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.80 & 0.83  & 0.95   & 0.95   & 0.89  & 1.00    & 0.96    & 0.89   \\
    $n$=50                   & 0.86 & 0.90  & 1.25   & 1.10   & 1.21  & 1.32    & 1.13    & 1.25   \\
    $n$=100                  & 1.02 & 1.04  & 1.58   & 1.20   & 1.54  & 1.67    & 1.24    & 1.63   \\
    $n$=300                  & 1.24 & 1.28  & 1.81   & 1.36   & 1.82  & 1.93    & 1.44    & 1.95   \\
    $n$=500                  & 1.25 & 1.29  & 1.80   & 1.33   & 1.84  & 1.91    & 1.39    & 1.97   \\ \hline
    $F$ = Bivariate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.77 & 0.79  & 0.92   & 0.92   & 0.86  & 0.96    & 0.92    & 0.85   \\
    $n$=50                   & 0.76 & 0.78  & 1.11   & 1.00   & 1.08  & 1.17    & 1.03    & 1.13   \\
    $n$=100                  & 0.78 & 0.79  & 1.27   & 1.06   & 1.33  & 1.35    & 1.11    & 1.41   \\
    $n$=300                  & 0.88 & 0.91  & 1.29   & 1.09   & 1.35  & 1.38    & 1.15    & 1.45   \\
    $n$=500                  & 0.93 & 0.96  & 1.37   & 1.13   & 1.40  & 1.44    & 1.19    & 1.48   \\ \hline
    $F$ = Bivariate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.70 & 0.72  & 0.83   & 0.84   & 0.77  & 0.89    & 0.87    & 0.79   \\
    $n$=50                   & 0.58 & 0.60  & 0.90   & 0.84   & 0.86  & 0.95    & 0.88    & 0.91   \\
    $n$=100                  & 0.57 & 0.59  & 0.92   & 0.87   & 0.97  & 0.98    & 0.90    & 1.03   \\
    $n$=300                  & 0.62 & 0.64  & 0.93   & 0.85   & 0.99  & 0.99    & 0.91    & 1.06   \\
    $n$=500                  & 0.62 & 0.65  & 0.93   & 0.86   & 1.00  & 1.00    & 0.92    & 1.08   \\ \hline
    $F$ = Bivariate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.66  & 0.76   & 0.78   & 0.72  & 0.81    & 0.81    & 0.73   \\
    $n$=50                   & 0.52 & 0.52  & 0.79   & 0.75   & 0.80  & 0.84    & 0.79    & 0.85   \\
    $n$=100                  & 0.51 & 0.52  & 0.83   & 0.77   & 0.88  & 0.88    & 0.81    & 0.94   \\
    $n$=300                  & 0.55 & 0.56  & 0.84   & 0.79   & 0.91  & 0.89    & 0.84    & 0.98   \\
    $n$=500                  & 0.56 & 0.59  & 0.85   & 0.80   & 0.93  & 0.91    & 0.86    & 0.99   \\ \hline
    $F$ = Bivariate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.63 & 0.65  & 0.77   & 0.79   & 0.74  & 0.80    & 0.81    & 0.74   \\
    $n$=50                   & 0.49 & 0.50  & 0.73   & 0.71   & 0.76  & 0.78    & 0.75    & 0.80   \\
    $n$=100                  & 0.45 & 0.46  & 0.73   & 0.69   & 0.81  & 0.78    & 0.73    & 0.87   \\
    $n$=300                  & 0.51 & 0.52  & 0.78   & 0.75   & 0.87  & 0.83    & 0.79    & 0.94   \\
    $n$=500                  & 0.53 & 0.55  & 0.79   & 0.75   & 0.87  & 0.84    & 0.80    & 0.94   \\ \hline
    $F$ = BVN                & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20                   & 0.56 & 0.60  & 0.69   & 0.71   & 0.67  & 0.73    & 0.74    & 0.68   \\
    $n$=50                   & 0.42 & 0.43  & 0.66   & 0.66   & 0.70  & 0.71    & 0.69    & 0.75   \\
    $n$=100                  & 0.42 & 0.43  & 0.69   & 0.66   & 0.77  & 0.74    & 0.71    & 0.83   \\
    $n$=300                  & 0.47 & 0.49  & 0.71   & 0.69   & 0.82  & 0.76    & 0.73    & 0.88   \\
    $n$=500                  & 0.48 & 0.50  & 0.73   & 0.71   & 0.83  & 0.78    & 0.76    & 0.89   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=2$}
\label{table:FSEtable2}
\end{table}

\begin{table}[t]
\begin{footnotesize}
   \begin{tabular}{c|cc|ccc|ccc}
    \hline
    3-variate $t_5$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.96 & 0.97  & 1.06   & 1.03   & 0.99  & 1.07    & 1.06    & 0.97   \\
    $n$=50             & 1.07 & 1.08  & 1.28   & 1.20   & 1.18  & 1.33    & 1.23    & 1.20   \\
    $n$=100            & 1.12 & 1.15  & 1.49   & 1.31   & 1.40  & 1.57    & 1.38    & 1.48   \\
    $n$=300            & 1.49 & 1.54  & 2.09   & 1.82   & 2.07  & 2.19    & 1.93    & 2.18   \\
    $n$=500            & 1.60 & 1.66  & 2.18   & 1.87   & 2.21  & 2.27    & 1.95    & 2.30   \\ \hline
    3-variate $t_6$    & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.90 & 0.92  & 1.00   & 0.99   & 0.95  & 1.02    & 1.01    & 0.94   \\
    $n$=50             & 0.95 & 0.96  & 1.16   & 1.09   & 1.09  & 1.21    & 1.14    & 1.11   \\
    $n$=100            & 0.98 & 0.99  & 1.32   & 1.22   & 1.25  & 1.38    & 1.27    & 1.29   \\
    $n$=300            & 1.10 & 1.14  & 1.57   & 1.40   & 1.58  & 1.62    & 1.47    & 1.64   \\
    $n$=500            & 1.17 & 1.20  & 1.57   & 1.43   & 1.60  & 1.63    & 1.51    & 1.67   \\ \hline
    3-variate $t_{10}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.87 & 0.88  & 0.95   & 0.94   & 0.90  & 0.97    & 0.98    & 0.89   \\
    $n$=50             & 0.77 & 0.79  & 0.96   & 0.92   & 0.94  & 0.99    & 0.96    & 0.95   \\
    $n$=100            & 0.75 & 0.76  & 1.02   & 0.95   & 1.01  & 1.06    & 1.00    & 1.05   \\
    $n$=300            & 0.73 & 0.75  & 1.03   & 0.98   & 1.10  & 1.08    & 1.03    & 1.15   \\
    $n$=500            & 0.73 & 0.76  & 1.02   & 0.98   & 1.09  & 1.06    & 1.02    & 1.14   \\ \hline
    3-variate $t_{15}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.84 & 0.86  & 0.92   & 0.92   & 0.89  & 0.94    & 0.94    & 0.87   \\
    $n$=50             & 0.75 & 0.76  & 0.92   & 0.90   & 0.90  & 0.96    & 0.94    & 0.93   \\
    $n$=100            & 0.66 & 0.67  & 0.91   & 0.87   & 0.95  & 0.96    & 0.92    & 1.00   \\
    $n$=300            & 0.61 & 0.64  & 0.90   & 0.87   & 1.00  & 0.93    & 0.91    & 1.04   \\
    $n$=500            & 0.65 & 0.67  & 0.89   & 0.87   & 0.99  & 0.93    & 0.91    & 1.03   \\ \hline
    3-variate $t_{25}$ & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.78 & 0.79  & 0.87   & 0.89   & 0.87  & 0.89    & 0.92    & 0.86   \\
    $n$=50             & 0.70 & 0.71  & 0.88   & 0.86   & 0.88  & 0.91    & 0.90    & 0.90   \\
    $n$=100            & 0.61 & 0.63  & 0.86   & 0.83   & 0.89  & 0.90    & 0.88    & 0.94   \\
    $n$=300            & 0.58 & 0.59  & 0.83   & 0.80   & 0.92  & 0.87    & 0.85    & 0.98   \\
    $n$=500            & 0.62 & 0.64  & 0.83   & 0.82   & 0.94  & 0.88    & 0.87    & 0.99   \\ \hline
    3-variate Normal   & SCM  & Tyler & HSD-CM & MhD-CM & PD-CM & HSD-wCM & MhD-wCM & PD-wCM \\ \hline
    $n$=20             & 0.76 & 0.78  & 0.85   & 0.87   & 0.84  & 0.87    & 0.90    & 0.83   \\
    $n$=50             & 0.66 & 0.67  & 0.82   & 0.81   & 0.84  & 0.86    & 0.86    & 0.86   \\
    $n$=100            & 0.56 & 0.58  & 0.77   & 0.75   & 0.83  & 0.82    & 0.79    & 0.87   \\
    $n$=300            & 0.53 & 0.55  & 0.75   & 0.74   & 0.85  & 0.79    & 0.78    & 0.90   \\
    $n$=500            & 0.56 & 0.58  & 0.76   & 0.76   & 0.87  & 0.80    & 0.80    & 0.92   \\ \hline
    \end{tabular}
\end{footnotesize}
\caption{Finite sample efficiencies of several scatter matrices: $p=3$}
\label{table:FSEtable3}
\end{table}
